A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2014-04-25 response/response.tex

\begin{center}
    {\LARGE \bf Point-by-Point Response to Reviewer's Comments} \\
     Author's Responses in {\color{red} Red}
\end{center}

%%%% First Reviewer %%%%
\section*{Re: Information to the authors}
%
\subsection*{I. Larger issues}
%
\begin{enumerate}
    \item Some parts of the manuscript suggest that the authors introduced a new method, i.e., the complex-step (CS) method. For example, in the introduction, they say ``A goal of this study was to develop and evaluate a new, accurate, and practical method ...'' Another example appears in page 3, where the authors say ``The aim of this paper is not only to introduce the new complex-step method in the context of evaluating tangent-stiffness matrices ...'' However, the CS method has already appeared in many publications since 1998 [1]. Please revise the way you refer to the CS method along the manuscript

{\color{red}
  \begin{itemize}
      \item In the cases of ambiguity pointed out by the reviewer, the wording has been changed such that it should be clear we are only evaluating an underutilized method, not introducing it.
  \end{itemize}
}
    \item
        The work presented focuses on a parallel computational peridynamic code, and
        uses peridynamic models for mechanics. However, no detailed explanation of the
        equations involved is presented. Although the tangent-stiffness calculations are
        not specialized to Peridigm, the authors should include a short section introducing
        the peridynamic theory and the specific constitutive model used, i.e., the elastic
        peridynamic solid. You may add this to the already included very brief description
        of peridynamics in page 9 (lines 15-26). This will also help to explain the concept
        of the peridynamic horizon in page 10.

{\color{red}
  \begin{itemize}
    \item 
        We have revised the brief description of peridynamics in page 9 to be more complete.
  \end{itemize}}

    \item 
        The manuscript seems to be written in a language more familiar to computer scientists. 
        I would encourage the authors to revise certain parts of the manuscript to be
        presented in a language more familiar to the computational mechanics community.

{\color{red}
  \begin{itemize}
    \item We have revised certain parts of the manuscript for clarity, adding additional information for the reader's convenience.
  \end{itemize}
  }

@@

  \item In Section 1.1.1, please include a more comprehensive literature review for
     the CS method, including further references (some of them are listed below).
     In particular, specify what aspects of the CS method have been investigated in
     each reference. Then, you need to clearly mention your contribution within
     the CS method, in contrast to the other references (some comments in this
     regard appear in the manuscript in page 8).

  {\color{red}
  \begin{itemize}
     \item The authors have appended a more comprehensive literature review for the CS method to section 1.1.1.  The aspects of CS investigated by the prior work, as well as any particularly interesting developments introduced by those works, have been listed. The literature review concludes with an argument for the novelty of this work.  
  \end{itemize}}

@@

  \item
      The comparisons of the different algorithms are only performed with respect to the
      construction of tangent-stiffness matrices. In particular, the authors always use the
      solution of AD at each time step to compute the entries of the tangent-stiffness
      matrices, even for the FD, CD, and CS methods. However, the authors need to
      demonstrate the performance of the CS method, in comparison to the other ones,
      with respect to the solution of real, ideally non-linear problems.

{\color{red}
  \begin{itemize}
    \item 
        To address the reviewers comment, additional simulation results are now included. New sections
        include "Simple example of CS, AD and FD for solution of nonlinear problems" with
        new subsections. To existing sections were appended new subsections
        including 'Convergence and displacement accuracy studies', 'Remarks for
        speed results' and 'Final Remarks'.
    \end{itemize}}

@@

\item 
      In other words, how the solutions compare in terms of accuracy and speed between the methods when
      solving given problems? Please include two examples of interest. The authors
      suggest that two examples involving non-linear systems are already included in the
      paper repository.

{\color{red}
  \begin{itemize}
    \item 
        The added section "Simple example of CS, AD and FD for solution of nonlinear problems" includes one of two examples (the second was omitted for brevity) alluded to in the manuscript and requested by the reviewer.  To summarize, in this section is an example of interest: a displacement accuracy study and a convergence rate study on a non-linear beam problem, where each of the methods discussed in the manuscript are used individually to solve the problem. 
 \end{itemize}}

@@

\item
      The authors say in the Conclusion: “While the results showed that CS
      produced more accurate tangent-stiffness matrices than CD and FD under
      the parameters of the tests, it was not determined whether or not this is
      a clear advantage of CS over FD in terms of accuracy of final predicted
      displacements and speed of convergence.” This needs to be studied and
      results in this regard added to this manuscript.

{\color{red}
  \begin{itemize}
    \item 
      The added subsection 'Convergence and displacement accuracy studies'
      includes convergence rate and displacement accuracy studies similar to
      those shown in `Simple example ...', but with the models and tools of
      the main study. This subsection provides an example of interest. 
  \end{itemize}}
  \end{enumerate}

@@

{\color{red}
  \begin{itemize}
      \item Footnote 1 has been added to manuscript to address this.
  \end{itemize}}

  \item
	Pg. 2: In line 36, what do you mean by “discrimination”?

{\color{red}  
\begin{itemize}
     \item

      The word, `discrimination' has been removed from the manuscript.
      'Discrimination' was meant to mean ``measuring differences and making
      judgements on relative usefulness''. Since this meaning is probably
      understood from the word `comparison' alone, the word `discrimination'
      has been removed from the manuscript for clarity.

@@

  \end{itemize}}

` \item	
	Pg. 2: In line 37, explain what do you mean by ``in-situ instrumentation''.

@@

{\color{red}  
\begin{itemize}
     \item
      The correction is made in the manuscript. An exact web address for the paper repository has been added.
  \end{itemize}}

  \item 
    Pg. 3: Please include the forward and centered ﬁnite difference expressions for
    easier comparison with (2); include the truncation error as well. You do not
    have to derive these expressions though.

{\color{red}  
\begin{itemize}
     \item
      The correction is made in the manuscript. Expressions for forward and centered difference have been included for faster comparison with (2).  
  \end{itemize}}

  \item 
Pg. 4: In Eq. (1), ``$\partial f^2$'' should be ``$\frac{\partial^2 f}{\partial x^2}$''; similarly, for the third derivative.

@@

{\color{red}  
\begin{itemize}
     \item
      The correction is made in the manuscript.
  \end{itemize}}

  \item 
Pg. 4: You may consider writing Eq. (2) with the truncation error

{\color{red}  
\begin{itemize}
     \item
      The correction is made in the manuscript.
  \end{itemize}}

\item
Pg. 6: In lines 9-11, please add references to the ``Poisson problem'' and to the
``mathematical optimization''.

{\color{red}  
\begin{itemize}
     \item
      The correction is made in the manuscript.

@@

  \end{itemize}}

\item
Pg. 7: Should Eqs. (4), (5), and (6) use ``$\approx$'' instead of “$=$”?

{\color{red}  
\begin{itemize}
     \item
         Manuscript corrected. These expressions are approximations.
  \end{itemize}}

\item
Pg. 7: In line 28, note that (cid:126)u is not the current conﬁguration, but the displacement
field. Please revise the sentence.

@@

{\color{red}  
\begin{itemize}
    \item
        Manuscript corrected. Sentence was revised to mean that F, evaluated in the current configuration, is a function of the displacement rather than to say that the displacement is the current configuration.
        \end{itemize}}

\item
Pg. 7: Please provide an expression for $F^{int}_i$ in the model used.

{\color{red}  
\begin{itemize}
    \item This is explained in words in Section 3.1.1
  \end{itemize}}

\item
Pg. 9: In line 26, please add the reference [12] below to ``coupling to molecular
simulations [29].''

@@

\item
Pg. 10: Please add an illustration of the block undergoing tension in Section 2.2,
for clarity. Also, clarify the displacement boundary conditions; are they applied in a
volumetric layer?

{\color{red}  
\begin{itemize}
    \item
        The manuscript has been corrected. Viewgraphs of the 2000 node and 1000000 node blocks undergoing tension has been included. The images depict colorized meshes in a way that is used in the revised manuscript to help explain what boundary conditions or 'volume constraints' are like in peridynamics. Displacement boundary conditions are typically applied to a volumetric layer, and in the study shown in the manuscript that is they way they were applied.
  \end{itemize}}

\item
Pg. 10: In line 40, you mentioned a bandwidth of 7. This seems to be clear in 1D.
Does this hold in higher dimensions? Please clarify.

{\color{red}  
\begin{itemize}
    \item
        This statement has been removed from the manuscript, it will not hold in 3D.
  \end{itemize}}

    \item
        In lines 47-49, you say ``The speciﬁc parameters ... can be found ... in the
        paper repository.'' It seems a good idea to have the paper repository with ﬁles that a
        user can eventually use. However, the content of the paper should be independent
        of the repository. Please include a table with the parameters used. Similarly, in
        page 11 (lines 11-13).

### 2014-04-25 jacobian_calc_CMAME.tex
AS SUBMITTED FOR REVISION

In solid and structural computational mechanics the tangent-stiffness matrix is a linearization operator that describes the stiffness of a system in response to small displacements imposed upon the current configuration of the system.  Mathematically speaking, the tangent-stiffness represents the gradient of a high-dimensional energy surface that ``points'' in the minimum direction. While the terminology of solid mechanics is used here, it's important to note that these operators appear in other physical settings and are known by other names, e.g. a \emph{transmissibility matrix} in the context of a Poisson problem or, more generally, a \emph{Jacobian matrix} in mathematical optimization.

>>>>

In solid and structural computational mechanics the tangent-stiffness matrix is a linearization operator that describes the stiffness of a system in response to small displacements imposed upon the current configuration of the system.  Mathematically speaking, the tangent-stiffness represents the gradient of a high-dimensional energy surface that ``points'' in the minimum direction. While the terminology of solid mechanics is used here, it's important to note that these operators appear in other physical settings and are known by other names, e.g. a \emph{transmissibility matrix} in the context of a Poisson problem or, more generally, a \emph{Jacobian matrix} in mathematical optimization \cite{morton2005numerical}.
